Essays in Computational Management Science

### 2018-05-21 Chapters/hathor-architecture.tex
Minor grammar mistakes.

This work introduces the Hathor's architecture, which lies between Bitcoin's and Iota's and may be a solution to scaling, centralization, and spam issues.

>>>>

This work introduces Hathor's architecture, which lies between Bitcoin's and Iota's and may be a solution to scaling, centralization, and spam issues.
